### 2024-12-15 papers.qmd
Update

<a href="https://hbr.org/2024/09/research-when-bonuses-backfire" style="border: 1px solid #007a04; color: #007a04; padding: 1px 8px; text-decoration: none; font-size: 0.7em; display: inline-block;">  WEB  </a>&nbsp;&nbsp;<br><br>

>>>>

<a href="https://hbr.org/2024/09/research-when-bonuses-backfire" style="border: 1px solid #007a04; color: #007a04; padding: 1px 8px; text-decoration: none; font-size: 0.7em; display: inline-block;">  WEB  </a>&nbsp;&nbsp;<button onclick="toggleAbstract('abstract-2024-Research:-When-Bonuses-Backfire')" style="border: 1px solid #007a04; color: #007a04; padding: 1px 8px; text-decoration: none; font-size: 0.7em; background: none; display: inline-block;">Abstract</button>
<div id="abstract-2024-Research:-When-Bonuses-Backfire" style="display:none; border: 1px solid #ccc; padding: 10px; margin-top: 10px;">Why do bonuses sometimes backfire? It’s because each incentive design choice both signals information about your own beliefs and intentions as an employer and shapes the signaling value of employee behavior within the organization. If you don’t think through these signals carefully, you may end up approving a bonus scheme with results that are the opposite of what you intend. This article offers a way to help you align the signals your incentive scheme sends with your performance goals.</div>
